The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-07 paper/paper.tex
paper: commit to intervals for now

Assuming $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\painting[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$, we can
mutually define the types $\restrftype[n][\lbrack 0,p-1 \rbrack]$ of frame
restrictions together with $\framep[n+1][0,...p]$ as a function from
$\restrf[n][\lbrack 0,p-1 \rbrack]$, introducing also abbreviations for the types
and definitions of layers, as well as for the combination of sequences
of $\framep[n][0,..,p-1]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and
$\restrf[n][\lbrack 0,p-1 \rbrack]$ in one block, which we call
$\depstype[n][0,...p-1]$:

@@

    \depstype[n][0,..,p-1]                    &        & \defeq            &

@@

Note that we write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the
projections of a $\deps$. Also, by abuse of notation, we write $\unitpoint$ for
the only inhabitant of $\depstype[n][0,..,0-1]$.

@@

    \depscohstype[n][0,..,p-1]              &                                     & \defeq                                                         &

@@

      (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][0,..,p-1]) :

@@

    (\depscohs[n][0,..,p])                  & \defeq                              &

@@

              (\depscohs[n][0,..,p-1]),                 \\

@@

                (\depscohs[n][0,..,p-1])(d), \restrl[n][p][q][\epsilon]
              (\depscohs[n][0,..,p])(d)(l)\right)       \\

@@

      (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][0,..,p-1])

@@

    \depscohs[n][0,..,p-1]

@@

             \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+2][p](\overline{\deps}(\depscohs[n][0,..,p-1])).\, \\
             \layer[n+1][p](\overline{\deps}(\depscohs[n][0,..,p-1])(d) \rightarrow                          \\

@@

             (\depscohs[n][0,..,p-1])(d))

@@

      (\depscohs[n][0,..,p]:\depscohstype[n][0,..,p]) :
    \restrltype[n][p] (\depscohs[n][0,..,p])}                                                                                                                                                                    \\

@@

    \depscohs[n][0,..,p]                    & \defeq                              &
    \lambda q\leq n. \lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][0,..,p-1])(d))(l \omega)} \\

@@

By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n][0,..,0-1]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).

@@

    \depscohttype[n][0,..,p-1]                                                               &                                                                               & \defeq                                                                            &

>>>>

Assuming $\framep[n][\lbrack 0,p-1 \rbrack]$ and $\painting[n][\lbrack 0,p-1 \rbrack]$ for $p \leq n+1$, we can
mutually define the types $\restrftype[n][\lbrack 0,p-1 \rbrack]$ of frame
restrictions together with $\framep[n+1][0,...p]$ as a function from
$\restrf[n][\lbrack 0,p-1 \rbrack]$, introducing also abbreviations for the types
and definitions of layers, as well as for the combination of sequences
of $\framep[n][\lbrack 0,p-1 \rbrack]$, $\painting[n][\lbrack 0,p-1 \rbrack]$ and
$\restrf[n][\lbrack 0,p-1 \rbrack]$ in one block, which we call
$\depstype[n][0,...p-1]$:

@@

    \depstype[n][\lbrack 0,p-1 \rbrack]       &        & \defeq            &

@@

Note that we write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the
projections of a $\deps$. Also, by abuse of notation, we write $\unitpoint$ for
the only inhabitant of $\depstype[n][\lbrack 0,0-1 \rbrack]$.

@@

    \depscohstype[n][\lbrack 0,p-1 \rbrack] &                                     & \defeq                                                         &

@@

      (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack]) :

@@

    (\depscohs[n][\lbrack 0,p \rbrack])     & \defeq                              &

@@

              (\depscohs[n][\lbrack 0,p-1 \rbrack]),           \\

@@

                (\depscohs[n][\lbrack 0,p-1 \rbrack])(d), \restrl[n][p][q][\epsilon]
              (\depscohs[n][\lbrack 0,p \rbrack])(d)(l)\right) \\

@@

      (\depscohs[n][\lbrack 0,p-1 \rbrack]:\depscohstype[n][\lbrack 0,p-1 \rbrack])

@@

    \depscohs[n][\lbrack 0,p-1 \rbrack]

@@

             \Pi q \leq n. \Pi \epsilon. \Pi d: \framep[n+2][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])).\, \\
             \layer[n+1][p](\overline{\deps}(\depscohs[n][\lbrack 0,p-1 \rbrack])(d) \rightarrow                          \\

@@

             (\depscohs[n][\lbrack 0,p-1 \rbrack])(d))

@@

      (\depscohs[n][\lbrack 0,p \rbrack]:\depscohstype[n][\lbrack 0,p \rbrack]) :
    \restrltype[n][p] (\depscohs[n][\lbrack 0,p \rbrack])}                                                                                                                                                                    \\

@@

    \depscohs[n][\lbrack 0,p \rbrack]       & \defeq                              &
    \lambda q\leq n. \lambda \epsilon.\,\lambda d.\lambda l.\overrightarrow{\cohf[n][p][q][q][\epsilon][\omega](d)}{\restrp[n][p][q][\epsilon](\restrf[n][p][q][\epsilon](\depscohs[n][\lbrack 0,p-1 \rbrack])(d))(l \omega)} \\

@@

By abuse of notation, we also write $E$ for an inhabitant of $\depscohstype[n][\lbrack 0,0-1 \rbrack]$ (standing for a non trivial inhabitant of $\fulldeps[n]$).

@@

    \depscohttype[n][\lbrack 0,p-1 \rbrack]                                                  &                                                                               & \defeq                                                                            &
